Solar wind prediction for the Parker Solar Probe orbit

### 2017-06-01 paperMVVB/sections/content.tex
added extrapolation figure draft; added some cites

%difference to other models
There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}, more cites?). They examine average values, additionally distinguishing between slow and fast wind. In this paper we instead look at the variations of the whole frequency distributions, consider solar activity and extrapolate these to the near-Sun region.\\

@@

In addition, the velocity is the defining parameter of the two types of solar wind. Solar wind mostly consists of and switches between slow and fast wind, whose ratio highly depends on solar activity. These types have different characteristics and their interactions lead to phenomena such as interaction regions. Additionally there also are coronal mass ejections (CMEs) embedded, whose occurrence rate follows solar activity too. Their share varies between almost zero in cycle minimum up to a half in maximum \citep{Richardson2012}. This study averages over these internal solar wind structures.

@@

%double lognormal fitting
%%%%%%%%%%%%%%%%%%%%%%%%%
%justification for compositional lognormal fit
To reach a better fit result for the velocity we change the fit function. We do not want to abandon the well-founded application of the lognormal function. However, it is reasonable to assume that the velocity distribution is composed of at least two branches (slow and fast). Therefore a compositional approach promises better fit results, which is why we combine two lognormal functions (\ref{eq:single_lognormal_fit_function}), bearing the disadvantage of more fit variables:
\begin{align}
	W_\text{II}(x) &= c \cdot W_1(x) + (1 -c) \cdot W_2(x)\,.	\label{eq:double_lognormal_fit_function}
\end{align}
The balancing parameter $c$ ensures that the resulting function remains normalized as it represents a probability distribution.

@@

The highest correlation coefficient for the magnetic field strength is 0.728. It is without lag time and the highest of all solar wind parameters, which is expected because the SSN is directly proportional to the solar surface magnetic flux (cite?).\\
Velocity and temperature have a lag time of 3~years with their maximal correlation coefficients (0.453 and 0.540). The density has a lag time of 6~years (0.468), which is in agreement with the by \citet{Bougeret1984} documented density anticorrelation with SSN.\\	%p.~406\\

@@

extrapolation errors...\\
Comparison with existing near-Sun models (renew extrapolation figure to 1-column; with half/twice SSN)\\
calculate or set min, avg and max SSN (e.g. 0, 100, 200)\\

>>>>

%difference to other models
There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}). They examine average values, additionally distinguishing between slow and fast wind. In this paper we instead look at the variations of the whole frequency distributions, consider solar activity and extrapolate these to the near-Sun region.\\

@@

In addition, the velocity is the defining parameter of the two types of solar wind. Solar wind mostly consists of and switches between slow and fast wind, whose different compositions and characteristics also indicate different sources and generation processes \citep{McGregor2011a} (better cites?). Their ratio highly depends on solar activity (cite?) and their interactions lead to phenomena such as interaction regions.

Additionally there also are coronal mass ejections (CMEs) embedded, whose occurrence rate follows solar activity too. Their share varies between almost zero in cycle minimum up to a half in maximum \citep{Richardson2012}. This study averages over these internal solar wind structures.

@@

%double lognormal fitting
%%%%%%%%%%%%%%%%%%%%%%%%%
%justification for compositional lognormal fit
To reach a better fit result for the velocity we change the fit function. We do not want to abandon the well-founded application of the lognormal function. However, it is reasonable to assume that the velocity distribution can be made up of at least two overlapping branches \citep{McGregor2011b}. Therefore a compositional approach promises better fit results, which is why we combine two lognormal functions (\ref{eq:single_lognormal_fit_function}), bearing the disadvantage of more fit variables:
\begin{align}
	W_\text{II}(x) &= c \cdot W_1(x) + (1 -c) \cdot W_2(x)\,.	\label{eq:double_lognormal_fit_function}
\end{align}
The balancing parameter $c$ ensures that the resulting function remains normalized as it represents a probability distribution.

@@

The highest correlation coefficient for the magnetic field strength is 0.728. It is without lag time and the highest of all solar wind parameters, which is expected because the SSN is directly proportional to the magnetic flux \citep{Smith2003}.\\
Velocity and temperature have a lag time of 3~years with their maximal correlation coefficients (0.453 and 0.540). The density has a lag time of 6~years (0.468), which is in agreement with the by \citet{Bougeret1984} documented density anticorrelation with SSN.\\	%p.~406\\

@@

Comparison with existing near-Sun models (Fig.~\ref{fig:sw_extrapolation_ssn_plot}); with half/twice SSN)\\
calculate or set min, avg and max SSN (e.g. 0, 100, 200)\\
\begin{figure*}
	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_plot.pdf}
	\caption{Solar wind model extrapolations to the PSP orbit region. The from Helios and OMNI measurements obtained models are extrapolated to the PSP region---for the case of solar minimum (maximum) with a SSN of 0 (200). For comparison other near-Sun models are also shown... to 1-column...?}
	\label{fig:sw_extrapolation_ssn_plot}
\end{figure*}

extrapolation errors...\\

\citep{Banaszkiewicz1998}, analytical magnetic field model, DQCS model\\
